A Simple Minibatch Acceptance Test for MCMC

### 2016-05-19 nips_2016.tex
Minor change, log likelihood --> likelihood
update author information

\author{
  Haoyu Chen \\
  Department of Computer Science \\
  University of California, Berkeley \\
  \texttt{haoyuchen@berkeley.edu}
  \And
  Daniel Seita \\
  Department of Computer Science \\
  University of California, Berkeley \\
  \texttt{seita@berkeley.edu}
  \And
  Xinlei Pan \\
  Department of Bioengineering \\
  University of California, Berkeley \\
  \texttt{xinleipan@berkeley.edu}
  \And 
  Biye Jiang \\
  Department of Computer Science \\
  University of California, Berkeley \\
  \texttt{bjiang@berkeley.edu}
  \And
  John Canny \\
  Department of Computer Science \\
  University of California, Berkeley \\
  \texttt{canny@berkeley.edu}
}

@@

The work of~\cite{conf/uai/MaclaurinA14} presents another minibatch MCMC method which gets the
\emph{exact} posterior, so long as there exists a (cheap) lower bound on the log likelihood for each
data point. Their approach is only a starting point, however, and it can be difficult to derive
these lower bounds in general cases. The extra auxiliary variables they introduce also hurt mixing.

@@

In this section, we explore the convergence properties of our MH test. We first introduce some
notation. Let our true and approximated acceptance probabilities be $P_a = g(\Delta) = \Pr(\Delta +
X > 0)$ and $P_a' = \Pr(\Delta' + X_{\rm corr} > 0)$.  Define $X_{\xi} = \varepsilon - X_{\rm norm}$
which means, invoking Equations~\ref{eq:relationship} and~\ref{eq:deconvolution}, that $X_\xi$ is
the random variable characterizing the accuracy of our $X_{\rm norm}$.  Thus, $\Delta' = \Delta +
X_{\rm norm} + X_\xi$. We assume the standard deviation of $X_{\rm norm}$ is less than
$\pi/\sqrt{3}$, so that we can use Equation~\ref{eq:deconvolution}. We denote $F_X(x)$ as the CDF of
$X$. (Note that $X$ is a \emph{scalar} random variable.)

>>>>

\author{
  Haoyu Chen \\
  Department of Computer Science \\
  University of California, Berkeley \\
  \texttt{haoyuchen@berkeley.edu}
  \And
  Daniel Seita \\
  Department of Computer Science \\
  University of California, Berkeley \\
  \texttt{seita@berkeley.edu}
  \And
  Xinlei Pan \\
  Graduate Program in Bioengineering \\
  UC Berkeley-UC San Francisco \\
  \texttt{xinleipan@berkeley.edu}
  \And 
  Biye Jiang \\
  Department of Computer Science \\
  University of California, Berkeley \\
  \texttt{bjiang@berkeley.edu}
  \And
  John Canny \\
  Department of Computer Science \\
  University of California, Berkeley \\
  \texttt{canny@berkeley.edu}
}

@@

The work of~\cite{conf/uai/MaclaurinA14} presents another minibatch MCMC method which gets the
\emph{exact} posterior, so long as there exists a (cheap) lower bound on the likelihood for each
data point. Their approach is only a starting point, however, and it can be difficult to derive
these lower bounds in general cases. The extra auxiliary variables they introduce also hurt mixing.

@@

In this section, we explore the convergence properties of our MH test. We first introduce some
notation. Let our true and approximated acceptance probabilities be $P_a = g(\Delta) = \Pr(\Delta +
X > 0)$ and $P_a' = \Pr(\Delta' + X_{\rm corr} > 0)$.  Define $X_{\xi} = \varepsilon - X_{\rm norm}$
which means, invoking Equations~\ref{eq:relationship} and~\ref{eq:deconvolution}, that $X_\xi$ is
the random variable characterizing the accuracy of our $X_{\rm norm}$.  Thus, $\Delta' = \Delta +
X_{\rm norm} + X_\xi$. We assume the standard deviation of $X_{\rm norm}$ is less than
$\pi/\sqrt{3}$, so that we can use Equation~\ref{eq:deconvolution}. We denote $F_X(x)$ as the CDF of
$X$.
